Manuscript Figures for Genome Biology (simulation subset)

### 2018-09-18 manuscript_figures/manuscript_figures_sims.Rmd

>>>>

# Supplementary Figure (informativeness covariates)

This is a faceted figure illustrating the functional relationship between the informative covariate and the the null proportion, pi0, when using either the continuous or discrete "informativeness" functions. The relationship is shown over a range of informativeness values for the two settings. These functions were used to investigate the impact of increasing/descreasing informativeness of the covariates while fixing other simulation conditions.

```{r SFigureSim6, fig.width = 12, fig.height = 4}
## SFigure Sim6 A: Informativeness covariate relationships (continuous)
cinfovar <- tibble(informativeness = seq(0, 1, by = 0.2))
cinfovar <- dplyr::mutate(cinfovar, x = list(seq(0, 1, .01)))
cinfovar <- dplyr::mutate(cinfovar, pi0 = lapply(informativeness, function(zz) pi0_varyinfo80l(zz)(x[[1]])))
cinfovar <- dplyr::mutate(cinfovar, informativeness = informativeness * 100)
cinfovar <- tidyr::unnest(cinfovar)

ps6a <- ggplot(cinfovar, aes(x = x, y = pi0)) +
    geom_line() +
    expand_limits(y = c(0.5, 1)) + 
    theme_classic() +
    scale_x_continuous(breaks = seq(0, 1, .2)) + 
    scale_y_continuous(labels = scales::percent) + 
    theme(axis.title = element_text(face = "bold", size = 10),
          plot.title = element_text(face = "bold", size = 14)) +
    facet_grid(. ~ informativeness, labeller = label_both)

## SFigure Sim6 B: Informativeness covariate relationships (discrete)
dinfovar <- tibble(informativeness = seq(0, 1, by = 0.2))
dinfovar <- dplyr::mutate(dinfovar, x = list(seq(0, 1, .01)))
dinfovar <- dplyr::mutate(dinfovar, pi0 = lapply(informativeness, function(zz) pi0_varyinfo80(zz)(x[[1]])))
dinfovar <- dplyr::mutate(dinfovar, informativeness = informativeness * 100)
dinfovar <- tidyr::unnest(dinfovar)

ps6b <- ggplot(dinfovar, aes(x = x, y = pi0)) +
    geom_line() +
    expand_limits(y = c(0.5, 1)) + 
    theme_classic() +
    scale_x_continuous(breaks = seq(0, 1, .2)) + 
    scale_y_continuous(labels = scales::percent) + 
    theme(axis.title = element_text(face = "bold", size = 10),
          plot.title = element_text(face = "bold", size = 14)) +
    facet_grid(. ~ informativeness, labeller = label_both)

## pull SFigure Sim6 together
SFigS6 <- plot_grid(ps6a, ps6b, labels = LETTERS[1:2], ncol = 1)
SFigS6
ggsave(file.path(outdir, "SFigureSim6.pdf"), width = 12, height = 4)
```
